Racial and Ethnic Differences in ETI: Outcomes

### 2024-07-07 Kamyron Jordan/Racial and Ethnic Differences in ETI/racial_and_ethnic_differences_in_eti_outcomes.qmd
maybe only use half the cores instead of 3/4

```{r}
invisible(lapply(continuous_outcomes), function(o) {
  f <- as.formula(paste0(
    o,
    "~ age_group + Insurance + bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
  ))
  m = lmer(f,data = encounter)
  predict_response(model = m, terms = c("Days[all]", "Race")) %>% plot()
})

```

>>>>

```{r}
invisible(lapply(continuous_outcomes), function(o) {
  f <- as.formula(paste0(
    o,
    "~ age_group + Insurance + bs(Days, knots = 0, degree = 1) * Race + (1 | eDWID)"
  ))
  m <- lmer(f, data = encounter)
  predict_response(model = m, terms = c("Days[all]", "Race")) %>% plot()
})
```
